Draft

### 2020-10-30 Final.Rmd
fixed the body paragraph of the thesis.

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{amsfonts}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
  - \usepackage{float}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

\pagebreak

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Building on previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk of a financial return and prediction of the VIX volatility index. Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter what the form of model misspecification. Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.

\pagebreak

@@

Assume the scoring rule is positively-oriented and the unknown parameters of the assumed predictive model are denoted as $\boldsymbol \theta \in \Theta$, and let $P^{t-1}_{\boldsymbol{\theta}}$ := $P(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the one-step-ahead predictive distribution function based on the assumed model where $\mathcal{F}_{t-1}$ represents all the information available at time $t-1$, and $p^{t-1}_{\boldsymbol{\theta}}$ := $p(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the corresponding predictive density function at time $t$. 
Then an estimator $\boldsymbol{\hat \theta}$ obtained by maximizing $\bar S(\boldsymbol{\theta})$ is said to be 'optimal' based on this scoring rule and $P^{t-1}_{\boldsymbol{\hat \theta}}$ is referred to as the optimal predictive. 
Specifically, we define 
\begin{equation} \label{eq:1}
\boldsymbol{\hat \theta} =arg \max_{\boldsymbol{\theta} \in \Theta} \bar S(\boldsymbol{\theta})
\end{equation}
where 
\begin{equation} \label{eq:sbar}
\bar S = \frac{1}{T-\tau+1}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
\end{equation}
with $\mathit{T}$ the total number of observations on a time series variable $y_t$ and $\tau$ the out-of-sample size. Under certain conditions, including that the scoring rule is proper and that the predictive model is correctly specified, $\boldsymbol{\hat \theta} \to \boldsymbol{\theta}_0 \ as \ \mathit{T} \to \infty$ where $\boldsymbol{\theta}_0$ represent the true (vector) parameter.

@@

*Table 1: The three simulation scenarios used in the numerical analysis. Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).*

@@

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 y_{t-1}^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
\end{tabular}}
\end{table}

@@

Copula models are a flexible way of representing the joint distribution function of a set of variables [@fan2014]. In recent years, these models have been applied to modelling serial dependence, which can be constructed as: 
\begin{equation} \label{eq:copula}
p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
\end{equation}
where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively, and c() is the copula density function that captures the dependence between $y_t$ and $y_{t-1}$.

For the simulation exercise, the marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while c() is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018. The stochastic volatility inversion copula model allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].

@@

We apply the scoring rules introduced in Section 2.2 and set CLS to focus on the 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in the following tables and figures. Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions. Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether optimal forecasts can provide benefits or not.

@@

Table 3 shows the results of Scenario (ii) where the assumed predictive model, ARCH(1), cannot capture the fat tails and volatility clustering feature of the data generated from the GARCH(1,1) model with Student-t error, i.e. the true DGP. Hence, there is misspecification. Tables 2 and 3 replicate some parts of the simulation results in previous literature; see @fbp2020, @optimal. Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%. The question is whether these characteristics of optimal forecasts will change if we move to a different form of model misspecification.

Table 4 shows another type of model misspecification, listed in Scenario (iii), where the ARCH(1) model cannot capture the asymmetric feature of the data generated from the stochastic volatility inversion copula model (the true DGP). Table 4 shows similar results as in Table 3. As the shape parameter decreases, the degree of negative marginal skewness increases, and optimal forecasts provide more benefits. Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification. ^[Tables are produced by R package: @kableextra and @knitr.]

*Table 2: It shows the results of Scenario (i), the correct model specification case. Both the true DGP and assumed predictive model are ARCH(1) with Gaussian error.*

@@

*Table 3: It corresponds to Scenario (ii) where the assumed predictive model is ARCH(1) with Gaussian error and the true DGP is GARCH(1,1) with Student-t error*

@@

*Table 4: It corresponds to Scenario (iii) where the assumed model is ARCH(1) with Gaussian error and the true DGP is stochastic volatility inversion copula.*

@@

@@

Accurate prediction of extreme values is important for financial risk management. Therefore, we provide score trace plots to exhibit the comparison of MLE, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails. The results in Section 3.2.1 show that when the degree of model misspecification is high, CLS can perform the best compared with MLE and CRPS in predicting both tails. However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.

In the left panel of each trace plot, it shows the performance of each score evaluated by CLS 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on the performance of predicting 90 percentile. From panels (a) and (b) in Figures 1 and 2, we can see that CLS almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as the misspecification increases, CLS starts to outperform CRPS and MLE in predicting tails. The more misspecified the model is, the more benefits can we gain from using CLS. Furthermore, more improvement in predictive accuracy occurs in the upper tail than in the lower tail, especially in Figure 2 where we have a negatively skewed marginal distribution. This result is consistent with @fbp2020. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

```{r}
# need to adjust the size. 
knitr::include_graphics("figure/figure1.pdf")
```

```{r}
knitr::include_graphics("figure/figure 2.pdf")
```

From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide the most benefits in improving prediction accuracy under the most misspecified case. In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 3. The shape of true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts, since predictions obtained from optimizing CLS aim to match the shape of tails of the true conditional predictive distributions. CLS focusing on upper tails (80%, 90%) is expected to perform poorly in the lower tail so the forecasters should have a clear expectation about what they aim to achieve [@fbp2020]. However, in practice, the shape of true conditional predictive distributions is usually unknown and it might create the difficulty of determining which tail we can reap more benefits from optimal forecasts without analysing a particular problem beforehand.

@@

@@

From the results in Section 3.2, we can conclude that optimal forecasts based on the CLS can improve the prediction accuracy in tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification. In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.

The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020.^[Data retrieved from @spdata] It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic. The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with initial training sample size = 1000 and out-of-sample evaluations = 5000.

The descriptive statistics in Table 5 show that the distribution of S&P 500 log returns is negatively skewed and has fat tails and strong serial correlation in its volatility. Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.^[Descriptive statistics are produced by R packages: @dplyr, @tidyverse, @tsibble, @tsibbledata, @feasts, @normtest, @moments.]

@@

```{r, results='hide'}
# descriptive statistics 
summary <- summary(logret$log.returns) # ----> need to be tabulated 
# range(logret$log.returns)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(logret$log.returns)
# Ljung box test
Box.test(logret$log.returns,lag = 2,type = "Lj",fitdf = 1)

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered",font_size = 10) %>% 
  add_header_above(c("Table 5: Descriptive statistics"=9))
```

@@

p3 <- logret %>% ACF((log.returns)^2) %>% autoplot() + 
  #ggtitle("Figure 11:Squared log returns autocorrelation")+
  xlab("number of lags")+ylab("ACF for variance")+theme_clean()
# +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")

figure <- ggarrange(p1,                                                 
          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
          nrow = 2, 
          labels = "A"                                        
          ) 
annotate_figure(figure, 
                top = text_grob("Descriptive figures",face = "bold"),
                fig.lab = "Figure 4",fig.lab.face = "bold"
                )
```

@@

From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’ and sufficiently misspecified model to forecast S&P 500 series and to observe the difference made by adopting optimal forecasts. The results in Table 6 show that the CLS outperforms other alternative scores in both lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3. However, the difference between using CLS10(80) and CLS20(90) is very small.

@@

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: Average scores for S&P 500"=7))
```

Unlike in the simulation example, the score trace plots now show how different scoring rules perform at time points that correspond to some actual historical events. In Figure 5, one interesting phenomenon is that after the GFC, the CLS performs much better than CRPS and MLE, in terms of predicting both upper and lower tails. It indicates that optimal probabilistic forecasts based on CLS can predict extreme events, such as the GFC, more accurately than other alternatives. This improvement brings up the average score of CLS optimizer after the GFC as shown in Figure 5. The difference between CLS and MLE/CRPS gets smaller and smaller over time until the recent COVID-19 pandemic. It is also worth noticing that CLS does not appear to provide more benefits in the upper tail than in the lower tail, which is different from the simulation results.^[The figures are produced by R packages: @ggplot2, @ggthemes, @ggpubr.]

>>>>

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes:
  - \usepackage{amsmath}
  - \usepackage{amsfonts}
  - \usepackage{setspace}\doublespacing
  - \usepackage[hyphens]{url}
  - \usepackage{float}
  - \usepackage[bottom]{footmisc}
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
link-citations: yes
bibliography: references.bib
---

@@

\newpage

@@

With correct model specification being a major challenge for conventional likelihood-based prediction, scoring rules have been used to produce forecasts that are accurate – in a well-defined sense - in the presence of misspecification. Building on previous research, this paper conducts numerical and empirical analyses to explore the impact of the form and degree of model misspecification on probabilistic forecasts that are optimal under a given score. In particular, we assess the predictive performance of optimal forecasts in two empirical contexts: prediction of the Value-at-Risk of a financial return and prediction of the VIX volatility index. Results show that the greater the degree of model misspecification, the more beneficial is optimal prediction, no matter what the form of model misspecification. Most notably, predictions that are optimal according to the censored likelihood score, which rewards predictive accuracy in a tail are substantially more accurate at predicting extreme events in said tail than the alternatives, including likelihood-based predictions.^[I would like to thank my supervisors: Professor Gael Martin and Dr. Ruben Loaiza-Maya, for the very constructive and detailed comments on my thesis and their support and help during this particularly difficult year.]

\newpage

@@

Assume the scoring rule is positively-oriented and the unknown parameters of the assumed predictive model are denoted as $\boldsymbol \theta \in \Theta$, and let $P^{t-1}_{\boldsymbol{\theta}}$ := $P(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the one-step-ahead predictive distribution function based on the assumed model where $\mathcal{F}_{t-1}$ represents all the information available at time $t-1$, and $p^{t-1}_{\boldsymbol{\theta}}$ := $p(\cdot|\mathcal{F}_{t-1},\boldsymbol \theta)$ be the corresponding predictive density function at time $t$. 
Then an estimator $\boldsymbol{\hat \theta}$ obtained by maximizing $\bar S(\boldsymbol{\theta})$ is said to be 'optimal' based on this scoring rule and $P^{t-1}_{\boldsymbol{\hat \theta}}$ is referred to as the optimal predictive. 
Specifically, we define 
\begin{equation} \label{eq:1}
\boldsymbol{\hat \theta} =arg \max_{\boldsymbol{\theta} \in \Theta} \bar S(\boldsymbol{\theta})
\end{equation}
where 
\begin{equation} \label{eq:sbar}
\bar S = \frac{1}{T-(\tau+1)}\sum_{t=2}^{T-\tau} S(P_{\boldsymbol{\theta}}^{t-1},y_t)
\end{equation}
with $\mathit{T}$ the total number of observations on a time series variable $y_t$ and $\tau$ the out-of-sample size. Under certain conditions, including that the scoring rule is proper and that the predictive model is correctly specified, $\boldsymbol{\hat \theta} \to \boldsymbol{\theta}_0 \ as \ \mathit{T} \to \infty$ where $\boldsymbol{\theta}_0$ represent the true (vector) parameter.

@@

@@

\textbf{Assumed model} & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ & $y_t = \mu +\sigma_t \epsilon_t$ \\ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ & $\sigma_t^2 = \alpha_0 + \alpha_1 (y_{t-1}-\mu)^2$ \\ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ & $\epsilon_t \sim N(0,1)$ \\ \hline
\end{tabular}}
\caption{The three simulation scenarios used in the numerical analysis. Scenario (i) represents correct model specification; Scenario (ii) represents a form of misspecification where the true DGP is GARCH with Student-t distribution while the assumed model is Gaussian ARCH(1); Scenario (iii) represents a more extreme form of misspecification, where the true DGP is an stochastic volatility model with a non-Gaussian marginal distribution while the assumed model is Gaussian ARCH(1).}
\end{table}

@@

Copulas are functions that describe the dependence between random variables or the serial dependence. Copula theory allows one to decompose the joint density of dependent random variables to the product of the marginal densities and the ‘copula density’ denoted as $c(\cdot)$, where the dependent structure is completely described by ‘copula density’. Since the marginal density and the copula does not require to be from the same family of distributions, it makes the choice of marginal density more flexible when one uses the copula-based models [@fan2014]. In this simulation, we aim to have a true DGP that captures two main features of financial returns – the volatility clustering and negative skewness in the marginal distribution. Thus, we only consider the use of copula in describing the serial dependence. Then the ‘decomposition’ can be represented as: 
\begin{equation} \label{eq:copula}
p_{t-1}(y_t)=c(P(y_t),P(y_{t-1}))p(y_{t-1})
\end{equation}
where $\mathit{P}()$ and $\mathit{p}$() denote the marginal distribution and density function of $y_t$ respectively.

Specifically, it is the stochastic volatility inversion copula model used in the simulation Scenario (iii). The marginal distribution $\mathit{P}()$ is chosen to be the standard skew-normal distribution, while $c(\cdot)$ is chosen to be the inversion copula of the stochastic volatility model described in @inversion2018. The stochastic volatility inversion copula model allows us to keep the dependence structure of a state space model and provides the flexibility of using an asymmetric marginal distribution that is often observed in financial returns [@inversion2018].

@@

We apply the scoring rules introduced in Section 2.2 and set CLS to focus on the 10%, 20%, 80% and 90% tails of the empirical marginal distribution, corresponding to the risks of long and short portfolios of financial investments, and we label them as CLS10, CLS20, CLS80 and CLS90 in the following tables and figures. Due to the fact that there is no reliable estimate of the true conditional densities, only the tails of the marginal distributions are set to be the standard when assessing the predictive accuracy by CLS, rather than the conditional distributions. Meanwhile, LS gives insights about the performance of the conventional likelihood-based methods and is used as a benchmark for comparing whether forecasts that are optimal according to alternative scoring rules can provide benefits or not.

@@

Table 3 shows the results of Scenario (ii) where the assumed predictive model, ARCH(1), cannot capture the fat tails and volatility clustering feature of the data generated from the GARCH(1,1) model with Student-t error, i.e. the true DGP. Hence, there is misspecification. Tables 2 and 3 replicate some parts of the simulation results in previous literature; see @fbp2020, @optimal. In Panels A and B of Table 3, when the degree of model misspecification is relatively low, the six optimizers cannot produce distinguishable enough probabilistic predictions to yield significantly different out-of-sample performance. There is no strict coherence observed. As the degree of model misspecification increases, in Panel C, the strict coherence is observed. The ARCH(1) model with Gaussian errors is now misspecified enough to let these optimisers produce very distinct predictions and the optimal prediction produced based on one scoring rule cannot be beaten out-of-sample according to that same scoring rule.

Optimal forecasts are expected to reap more benefits as the degree of model misspecification increases, and predictions based on CLS at 80% and 90% perform poorly when assessed by LS, CRPS, CLS at 10% and CLS at 20%. The question is whether these characteristics of optimal forecasts will change if we move to a different form of model misspecification.

Table 4 shows another type of model misspecification, listed in Scenario (iii), where the ARCH(1) model cannot capture the asymmetric feature of the data generated from the stochastic volatility inversion copula model (the true DGP). Table 4 shows similar results as in Table 3. In Panel A, when the true DGP is symmetric (shape = 0), optimal predictions are non-distinguishable and hence, yield very similar out-of-sample performance. There are no significant benefits reaped from using optimal probabilistic forecasts. However, as the shape parameter decreases, the degree of negative marginal skewness increases, as shown in Panels B and C, optimal predictions produced are more different from each other and yield different average out-of-sample scores. Even though, strictly speaking, we do not observe strict coherence in Panel C, the most misspecified case, it is close enough to conclude that optimal forecasts perform in the same way even when we have different forms of model misspecification. ^[Tables are produced by R package: @kableextra and @knitr.]

@@

Table 2: Average out-of-sample scores under the correctly specified ARCH(1) model with Gaussian errors, corresponding to Scenario (i) in Table 1. The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer. The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.

@@

Table 3: Average out-of-sample scores under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (ii) in Table 1. The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer. The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function. Panel A, B and C shows the average out-of-sample scores of the true DGP - GARCH(1,1) with $t_{\nu=35}$, $t_{\nu=12}$, $t_{\nu=3}$ errors.

@@

Table 4: Average out-of-sample scores under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (iii) in Table 1. The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer. The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function. Panel A, B and C shows the average out-of-sample scores of the true DGP – stochastic volatility inversion copula model with shape parameter specified as {0, -3, -5} respectively.

@@

Accurate prediction of extreme values is important for financial risk management. Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and CLS’s performance in predicting the 10 percentile and 90 percentile in Figure 1 and 2 so that we can evaluate their performance in predicting tails. The trace plots demonstrate the cumulative average out-of-sample score over an expanding evaluation period of CLS10 (left panel) and CLS90 (right panel) for four optimizers \{LS, CRPS, CLS10(80), CLS20(90)\}. The results in Section 3.2.1 show that when the degree of model misspecification is high, CLS can perform the best compared with LS and CRPS in predicting both tails. However, only the average score values at the end of each iteration of the simulation are recorded in the tables, while trace plots provide a dynamic view of how optimal forecasts perform.

In the left panel of each trace plot, it shows the performance of each score evaluated by CLS 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on the performance of predicting 90 percentile.

Figure 1 shows the correct specification case, corresponding to Scenario (i) and Table 2, it is impossible to distinguish these 4 lines in both lower and upper tails, which suggests that the cumulative average out-of-sample scores of these four optimisers are almost identical. It indicates that their out-of-sample performance are almost the same over the expanding evaluation period. Figure 2 corresponds to Scenario (ii) and Table 3 where the ARCH(1) model is misspecified for the GARCH(1,1) model with Student-t error. In panels (a) and (b), the least misspecified case, we can see that CLS almost makes no difference compared with other scoring rules, but as the misspecification increases, in panels (c) to (f), CLS starts to outperform CRPS and LS in predicting tails. Especially in panels (e) and (f), the gap between CLS10/90 (the blue line) and LS (the green line) is easily observed, which indicates that the more misspecified the model is, the more benefits can we gain from using CLS. Similar findings can be observed in Figure 3, which shows another type of model misspecification as in Scenario (iii). The increasing gap between CLS90 and LS, in panels (c) to (f), suggests that CLS makes more improvement in terms of the prediction accuracy in tails as the degree of model misspecification increases. Furthermore, the gap between CLS10/90 and LS tends to be bigger in the upper tail, compared with in the lower tail, especially in Figure 3. It suggests that more improvement is made in predictive accuracy occurs in the upper tail than in the lower tail. This result is consistent with @fbp2020. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

```{r,fig.align="center"}
# need to adjust the size. 
knitr::include_graphics("figure/figure1.pdf")
```

Figure 1: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the correctly specified ARCH(1) model with Gaussian errors, corresponding to Scenario (i) in Table 1. 
```{r}
knitr::include_graphics("figure/figure 2.pdf")
```

Figure 2: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (ii) in Table 1. The two subplots in each row represents the cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) of the true DGP – GARCH(1,1) with $t_{\nu=35}$, $t_{\nu=12}$, $t_{\nu=3}$ errors.

```{r}
knitr::include_graphics("figure/figure 3.pdf")
```

Figure 3: Cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) over an expanding evaluation period under the misspecified ARCH(1) model with Gaussian errors, corresponding to Scenario (iii) in Table 1. The two subplots in each row represents the cumulative average out-of-sample scores of CLS10 (left panel) and CLS90 (right panel) of the true DGP – stochastic volatility inversion copula model with shape parameter specified as {0, -3, -5} respectively.

From the average out-of-sample score tables and trace plots above, we can see that optimal forecasts provide the most benefits in improving prediction accuracy under the most misspecified case. In order to provide a more complete view of how optimal forecasts work, the predictive densities of the most misspecified case are plotted in Figure 4. The shape of true conditional predictive distributions plays a role in deciding how much we can gain by using optimal forecasts, since predictions obtained from optimizing CLS aim to match the shape of tails of the true conditional predictive distributions.

In the left panel of Figure 4, CLS90 (the red line) matches the shape of the upper tail of the true distribution (the pink line) perfectly but did a very poor job in predicting the lower tail. It is the same for CLS10 (the blue line) to match the shape of the lower tail of the true distribution perfectly. This visualizes how CLS reward the prediction accuracy in the region of interest to the forecaster. While in the right panel of Figure 4, it shows another type of model misspecification, and CLS does not manage to match the shape of the tails of the true distribution, but it still does a better job than LS in both tails. This suggests that when it comes to determining when the optimal probabilistic forecasts work, it actually depends on the shape of the true distribution, the assumed model specification, and the scoring rules. However, in practice, the shape of true conditional predictive distributions is usually unknown and it might create the difficulty of determining which tail we can reap more benefits from optimal forecasts without analysing a particular problem beforehand.

@@

Figure 4: The conditional predictive density produced by LS, CLS10 and CLS90 under the misspecified ARCH(1) model with Gaussian errors, corresponding to Panel C in Tables 3 and 4. The left panel is the conditional predictive density at a randomly picked time $t = 2001$ with the true DGP as stochastic volatility inversion copula (shape = -3), and the right panel is the conditional predictive density at a randomly picked time $t = 2501$ with the true DGP as GARCH(1,1) with $t_{\nu = 3}$ errors.

@@

From the results in Section 3.2, we can conclude that optimal forecasts based on the CLS can improve the prediction accuracy in the tails and its effect is clearest when the degree of model misspecification is high and does not vary much when we have different types of model misspecification. In Section 4, we apply the same method adopted in Section 3 to an empirical setting and investigate how it performs in practice.

The data used in the analysis is the continuously compounded daily log returns of S&P 500 listed in U.S.A financial market over a broad time period from 27 September,1996 to 30 July,2020.^[Data retrieved from @spdata] It aims to include two very volatile periods, the GFC and the recent COVID-19 pandemic. The initial training sample size and out-of-sample observations are kept consistent with what is in Section 3 with an initial training sample size of 1000 and out-of-sample evaluations of 5000.

The descriptive statistics in Table 5 show that the distribution of S&P 500 log returns is negatively skewed, has fat tails and strong serial correlation in its volatility. Moreover, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.^[Descriptive statistics are produced by R packages: @dplyr, @tidyverse, @tsibble, @tsibbledata, @feasts, @normtest, @moments.]

@@

```{r, results='hide'}
# descriptive statistics 
summary <- summary(logret$log.returns) # ----> need to be tabulated 
# range(logret$log.returns)
# some test results aginst normal dist h_null
# JB test
jb.norm.test(logret$log.returns)
# qchisq(.95, df=2)
# Ljung box test
Box.test((logret$log.returns)^2,lag = 2,type = "Lj",fitdf = 1)
# qchisq(.95, df=lags)

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=27066,LB.Test=1742.7)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered",font_size = 10) %>% 
  add_header_above(c("Table 5: Descriptive statistics for S&P500 log returns"=9))
```

Table 5: Descriptive statistics for S&P 500 index log returns. The Min and Max are the smallest and largest value of the sample series, respectively. Skewness is a measure of the asymmetry and kurtosis is a measure of fat tails with the normal distribution having kurtosis equals to three.  ‘JB.Test’ is the test statistic for the Jarque-Bera test of normality, with a critical value of 5.99. ‘LB.Test’ is the test of serial correlation of the squared returns, with a critical value based on 2 lags as 5.99.

@@

p3 <- logret %>% ACF((log.returns)^2) %>% autoplot() + 
  #ggtitle("Figure 11:Squared log returns autocorrelation")+
  xlab("number of lags")+ylab("ACF of squared returns")+theme_clean()
# +labs(caption = "Figure 11: the autocorrelation plot shows there is a strong serial correlation in volatility of S&P500")

figure <- ggarrange(p1,                                                 
          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
          nrow = 2, 
          labels = "A"                                        
          ) 
annotate_figure(figure, 
                top = text_grob("Descriptive figures for S&P500 log returns",face = "bold"),
                fig.lab = "Figure 5",fig.lab.face = "bold"
                )
```

Figure 5: The descriptive figures for S&P 500 log returns. Panel A is the time series plot of S&P 500 log returns. High volatility is observed during the GFC and the recent COVID-19 pandemic. Panel B is the histogram which illustrates the estimated marginal distribution of log returns. Panel C represents the autocorrelation function (ACF) plot of the squared returns, which indicates strong autocorrelation in volatility of log returns.

@@

From the wide-usage of ARCH models in modelling financial returns and volatility, and the strict coherence observed in Section 3.2.1, ARCH(1) should be a ‘compatible’, but sufficiently misspecified model to forecast S&P 500 series and to observe the difference made by adopting optimal forecasts. The results in Table 6 show that the CLS outperforms other alternative scores in both the lower and upper tails, which closely follows the results and conclusions drawn in the numerical analysis in Section 3. However, the difference between using CLS10(80) and CLS20(90) is very small.

@@

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `CLS10` = cell_spec(format(`CLS10`,4),"latex",bold = ifelse(`CLS10`==max(`CLS10`),TRUE,FALSE)),
    `CLS20` = cell_spec(format(`CLS20`,4),"latex",bold = ifelse(`CLS20`==max(`CLS20`),TRUE,FALSE)),
    `CLS80` = cell_spec(format(`CLS80`,4),"latex",bold = ifelse(`CLS80`==max(`CLS80`),TRUE,FALSE)),
    `CLS90` = cell_spec(format(`CLS90`,4),"latex",bold = ifelse(`CLS90`==max(`CLS90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 6: Average scores for S&P 500 log returns"=7))
```

Table 6: Average out-of-sample scores for S&P log returns, under the misspecified Gaussian ARCH(1) model. The row names are the in-sample optimizers used in producing the probabilistic forecasts and the column names are the criterion functions used to evaluate the out-of-sample performance of the probabilistic forecasts produced by each optimizer. The bolded value is the column maximum indicating the best performing optimiser according to the out-of-sample criterion function.
